### 2023-05-22 paper/paper.tex
Formatting, add title etc

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

@@

\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{example.bib} % The filename of the bibliography

@@

@@

\thesistitle{Thesis Title} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Dr. James \textsc{Smith}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Master of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{John \textsc{Smith}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Data Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.ucu.edu.ua}{Ukrainian Catholic University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{http://department.university.com}{Faculty of Applied Sciences}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{\href{http://researchgroup.university.com}{Department of Computer Sciences}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{http://faculty.university.com}{}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

@@

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{http://www.johnsmith.com}{\authorname} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\href{http://www.jamessmith.com}{\supname} % Supervisor name - remove the \href bracket to remove the link  
\end{flushright}
\end{minipage}\\[3cm]

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
\end{abstract}

@@

\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)

\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\

\end{abbreviations}

@@

\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table

% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it

Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
%Constant Name & $Symbol$ & $Constant Value$ with units\\

\end{constants}

@@

\begin{symbols}{lll} % Include a list of Symbols (a three column table)

$a$ & distance & \si{\meter} \\
$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
%Symbol & Name & Unit \\

\addlinespace % Gap to separate the Roman symbols from the Greek

$\omega$ & angular frequency & \si{\radian} \\

\end{symbols}

@@

@@

\include{Appendices/AppendixA}
%\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}

>>>>

% \usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters

@@

% \usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[backend=biber,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{references.bib} % The filename of the bibliography

@@

\usepackage{todonotes}

@@

\thesistitle{Corner localization and camera calibration from imaged lattices} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Dr. James \textsc{Pritts}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Master of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Andrii \textsc{Stadnik}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Data Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.ucu.edu.ua}{Ukrainian Catholic University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
% \department{\href{http://department.university.com}{Faculty of Applied Sciences}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
% \group{\href{http://researchgroup.university.com}{Department of Computer Sciences}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
% \faculty{\href{http://faculty.university.com}{}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
\department{Faculty of Applied Sciences} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{Department of Computer Sciences} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

@@

		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushleft} \large
				\emph{Author:}\\
				% \href{http://www.johnsmith.com}{\authorname} % Author name - remove the \href bracket to remove the link
				\authorname % Author name - remove the \href bracket to remove the link
			\end{flushleft}
		\end{minipage}
		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushright} \large
				\emph{Supervisor:} \\
				\href{https://prittjam.github.io/}{\supname} % Supervisor name - remove the \href bracket to remove the link  
			\end{flushright}
		\end{minipage}\\[3cm]

@@

\begin{abstract}
	\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
	The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots

	% Camera calibration is a crucial step in many computer vision applications.
	% However, despite the constant development of solutions, they still tend to
	% be sensitive to the noise of the input data, bad lightning conditions,
	% occlusions and other problems, especially under the conditions of
	% high distortion, such as mobile phones and GoPro-type cameras.
	%
	% In this paper, we propose a novel approach to camera calibration. We want to
	% use a robust solver to estimate the geometry between the correspondence of
	% points on the calibration pattern, which are called conjugate translations.
	% It is possible to use those
	% conjugate translations to predict the possible position of the previously
	% undetected calibration board features. We want to use the new points to constrain the camera calibration further. This process can be run iteratively,
	% refining the calibration board features, conjugate translations, and improving
	% the camera calibration.
\end{abstract}

@@

% \begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
%
% 	\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
% 	\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\
%
% \end{abbreviations}

@@

% \begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table
%
% 	% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it
%
% 	Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
% 	%Constant Name & $Symbol$ & $Constant Value$ with units\\
%
% \end{constants}

@@

% \begin{symbols}{lll} % Include a list of Symbols (a three column table)
%
% 	$a$ & distance & \si{\meter} \\
% 	$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
% 	%Symbol & Name & Unit \\
%
% 	\addlinespace % Gap to separate the Roman symbols from the Greek
%
% 	$\omega$ & angular frequency & \si{\radian} \\
%
% \end{symbols}

@@

\listoftodos{1}
\todo{Remove list of todos}

@@

% \include{Appendices/AppendixA}
%\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}
